Ceph Parallel File System Evaluation Report

### 2013-10-03 abstract.tex
Minor corrections

Ceph is an emerging open-source parallel distributed file and storage
system. By design, Ceph is designed to leverage unreliable and commodity
storage and network hardware, and provides reliability and fault-tolerance
via controlled object placement and data replication.  
%Here we evaluate Ceph
%for scientific high-performance computing (HPC) environments.  
This paper
presents our file and block I/O performance and scalability evaluation of Ceph for
scientific high-performance computing (HPC) environments.
% methodology, experiments, results and observations from
%mostly parallel I/O performance and scalability perspectives.  
Our work makes
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should benefit both Ceph and the HPC community
at large. 
%Throughout the evaluation, we observe that Ceph is an evolving
%technology under fast-paced development and shows great promises.

>>>>

Ceph is an emerging open-source parallel distributed file and storage
system. By design, Ceph leverages unreliable commodity
storage and network hardware, and provides reliability and fault-tolerance
via controlled object placement and data replication.  
%Here we evaluate Ceph
%for scientific high-performance computing (HPC) environments.  
This paper
presents our file and block I/O performance and scalability evaluation of Ceph for
scientific high-performance computing (HPC) environments.
% methodology, experiments, results and observations from
%mostly parallel I/O performance and scalability perspectives.  
Our work makes
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should benefit both Ceph and the HPC community
at large. 
%Throughout the evaluation, we observe that Ceph is an evolving
%technology under fast-paced development and shows great promises.

### 2013-10-03 baseline.tex
Minor corrections

Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
Because our entire testbed is built on IB QDR fabric (including client to
server host connections over a 108-port Mellanox IB QDR switch), we used IP
over IB (IPoIB) for networking\footnote{As of writing of this report, Inktank
is investigating using rsockets to improve performance with IB fabric}. Through
simple \verb!netperf! tests, we observed that a pair of hosts connected by IB
QDR using IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per
recommendations from Mellanox). With all four server hosts (OSD servers), we
expect the aggregate throughput to be in the neighborhood of 11 GB/s.

>>>>

Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
Because our entire testbed is built on IB QDR fabric (including client to
server host connections over a 108-port Mellanox IB QDR switch), we used IP
over IB (IPoIB) for networking\footnote{As of writing of this paper, Inktank
is investigating using rsockets to improve performance with IB fabric}. Through
simple \verb!netperf! tests, we observed that a pair of hosts connected by IB
QDR using IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per
recommendations from Mellanox). With all four server hosts (OSD servers), we
expect the aggregate throughput to be in the neighborhood of 11 GB/s.
